Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2022-12-20 paper_comparison/paper_comparison/paper_comparison.Rmd
discuss choices of tests and mention pkgs

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with $X_{raw} \sim U(-1,1)$, against the natural logarithm of the effect $log_e(E)$ with comparison to the power of an exact test - RESET test, and two other residual-based conventional tests commonly used in regression diagnostics but for testing heteroskedasticity and non-normality respectively.
For the RESET test, we included different power of fitted values as proxies. According to [@ramsey_tests_1969], there is no general rule for the power of the fitted values needed by the RESET test, but it found power up to four is usually sufficient. Thus, we followed this guidline to conduct the RESET test.

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with $X_{raw} \sim U(-1,1)$, against the natural logarithm of the effect $log_e(E)$.

As discussed in Section \ref{conventionally-testing-for-departures}, many conventionally tests are available for detecting residual departures. Implementation-wise, the built-in R package `stats` provides some commonly used residual-based tests, such as Shapiro-Wilk test. A more comprehensive collection of regression diagnostics tests can be found in the R package `lmtest` [@lmtest]. In terms of heteroskedasticity diagnostics, the R package `skedastic` [@skedastic] collects and implements 25 existing conventional tests published since 1961.

To compare the power of visual test and conventional tests, we picked RESET test (`resettest`) and Breusch-Pagan test (`bptest`) from the R package `lmtest`, and Shapiro-Wilk test (`shapiro.test`) from the built-in R package `stats`. These three tests can be used to detect non-linearity, heteroskedasticity and non-normality respectively. Their estimated power is shown in Figure \ref{fig:polypower}. For the RESET test, we included different power of fitted values as proxies. According to [@ramsey_tests_1969], there is no general rule for the power of the fitted values needed by the RESET test, but it found power up to four is usually sufficient. Thus, we followed this guideline to conduct the RESET test. For the Breusch-Pagan test, both $\boldsymbol{x}$ and $\boldsymbol{x}^2$ were included in the auxiliary regression equation to [justify this choice?].

### 2022-12-20 paper_comparison/paper_comparison/paper_comparison.tex
discuss choices of tests and mention pkgs

Figure \ref{fig:polypower} shows the estimated power of visual test on
lineups produced by the non-linearity model with
\(X_{raw} \sim U(-1,1)\), against the natural logarithm of the effect
\(log_e(E)\) with comparison to the power of an exact test - RESET test,
and two other residual-based conventional tests commonly used in
regression diagnostics but for testing heteroskedasticity and
non-normality respectively. For the RESET test, we included different
power of fitted values as proxies. According to
\citep{ramsey_tests_1969}, there is no general rule for the power of the
fitted values needed by the RESET test, but it found power up to four is
usually sufficient. Thus, we followed this guidline to conduct the RESET
test.

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on
lineups produced by the non-linearity model with
\(X_{raw} \sim U(-1,1)\), against the natural logarithm of the effect
\(log_e(E)\).

As discussed in Section \ref{conventionally-testing-for-departures},
many conventionally tests are available for detecting residual
departures. Implementation-wise, the built-in R package \texttt{stats}
provides some commonly used residual-based tests, such as Shapiro-Wilk
test. A more comprehensive collection of regression diagnostics tests
can be found in the R package \texttt{lmtest} \citep{lmtest}. In terms
of heteroskedasticity diagnostics, the R package \texttt{skedastic}
\citep{skedastic} collects and implements 25 existing conventional tests
published since 1961.

To compare the power of visual test and conventional tests, we picked
RESET test (\texttt{resettest}) and Breusch-Pagan test (\texttt{bptest})
from the R package \texttt{lmtest}, and Shapiro-Wilk test
(\texttt{shapiro.test}) from the built-in R package \texttt{stats}.
These three tests can be used to detect non-linearity,
heteroskedasticity and non-normality respectively. Their estimated power
is shown in Figure \ref{fig:polypower}. For the RESET test, we included
different power of fitted values as proxies. According to
\citep{ramsey_tests_1969}, there is no general rule for the power of the
fitted values needed by the RESET test, but it found power up to four is
usually sufficient. Thus, we followed this guideline to conduct the
RESET test. For the Breusch-Pagan test, both \(\boldsymbol{x}\) and
\(\boldsymbol{x}^2\) were included in the auxiliary regression equation
to {[}justify this choice?{]}.
